Prior work on autonomous LLM agents has advanced several ingredients of long-horizon execution, including action interfaces, memory, self-improvement, and web interaction. Our position relative to this literature is more specific than a generic ``integrated system'' claim. GA is built around a single systems objective, \emph{maximizing contextual information density}, and studies how multiple agent components should be co-designed when the bottleneck is not raw capability but how much decision-relevant information can be preserved within a limited context budget. In this sense, GA is not simply a new memory module, a new reflection method, or a new browser agent; it is a general-purpose agent architecture that connects these ingredients through a common optimization target.

\subsection{LLM-Based Agent Systems and Action Interfaces}
\label{sec:related_llm_agents}

LLM agents have evolved from prompt-level reasoning loops to integrated systems that execute long action sequences in real environments. ReAct~\citep{react} and Reflexion~\citep{reflexion} established the basic loop of interleaving reasoning, acting, and feedback. AutoGPT~\citep{autogpt} popularized iterative goal decomposition, while MetaGPT~\citep{metagpt} pushed the field toward explicit multi-role coordination and workflow design. This line established the key intuition that agent performance depends not only on the base model, but also on how deliberation is scaffolded over multiple steps.

As agents moved into software engineering and computer-use settings, the action interface itself became a first-class design choice. CodeAct~\citep{codeact} unifies agent actions as executable code, which increases compositional flexibility and makes behaviors easier to test and reuse. Devin~\citep{devin}, SWE-agent~\citep{sweagent}, and OpenHands~\citep{openhands} further show that performance depends strongly on how the model is connected to the external environment, whether through integrated coding workflows, specialized Agent--Computer Interfaces, or open agent runtimes. Recent product systems such as Claude Code~\citep{claudecode}, Codex~\citep{codex}, Manus~\citep{manus}, and OpenClaw~\citep{openclaw_rl} reinforce the same trend in practice.

GA is closest to this systems line, but differs in what it optimizes. Most existing agent systems primarily expand reachable behaviors through richer workflows, more specialized tools, or stronger environment integration. By contrast, GA asks how broad computer-use capability can be preserved while keeping the action space and prompt overhead deliberately small. Its minimal atomic toolset is therefore not just an implementation choice, but part of the paper's central claim: cross-domain long-horizon performance can improve when tool abstraction is designed to increase contextual information density rather than to maximize interface richness.

\subsection{Memory and Context Management}
\label{sec:related_memory}

A second line of work studies how agents retain only behaviorally useful information as trajectories grow. MemGPT~\citep{memgpt} treats the context window as a limited working memory and external storage as archival memory, introducing a paging-style view of agent memory. A-MEM~\citep{amem} instead models memory as a dynamically evolving network of atomic notes and links, enabling richer associative recall. These approaches make long-horizon agents more feasible, but they focus primarily on storage and retrieval.

Recent work increasingly treats context construction itself as a systems problem. LongLLMLingua~\citep{longllmlingua} shows that prompt compression can preserve task-relevant information while reducing long-context cost, and practical context-engineering analyses emphasize that agent quality depends not only on window length but also on what enters the window and in what form~\citep{anthropic_context}. Production systems such as Claude Code~\citep{claudecode} and Manus~\citep{manus} similarly rely on artifact-based tracking and periodic compaction to extend effective horizon.

GA differs from both memory-centric and compression-centric approaches in two ways. First, it treats memory quality as a \emph{verification and selection} problem, not only a storage or retrieval problem: only behavior-changing and validated information is promoted into longer-term representations. Second, it optimizes the full path from observation to retained memory, rather than only the final retrieval step. The resulting design goal is not to keep more history accessible, but to keep the active context as sparse, reliable, and decision-relevant as possible.

\subsection{Self-Evolution and Experience Distillation}
\label{sec:related_self_evolution}

Research on self-evolving agents asks how repeated execution can become future capability. A recent survey~\citep{selfevolvesurvey} organizes the space by what evolves, when evolution happens, and what feedback drives improvement. Within this space, Agent-Pro~\citep{agentpro} studies policy-level reflection and optimization, showing that agents can revise their own behavioral policies without updating model parameters. Voyager~\citep{voyager} demonstrates a stronger form of accumulation in a specialized environment by continually storing verified executable skills.

Broader general-purpose work mostly evolves the agent through textual abstractions. EvolveR~\citep{evolver}, FLEX~\citep{flex}, AgentEvolver~\citep{agentevolver}, and experience-driven lifelong learning~\citep{selfevolvinglifelong} all convert trajectories into strategic principles, reflections, or structured knowledge units that help later execution. This is an important step beyond simple history reuse, but in most cases the retained experience remains natural-language guidance rather than executable capability.

GA is aligned with this line in viewing reflection as the engine of continual improvement, but it makes a stronger systems claim: the endpoint of reflection should be a \emph{representation shift} from verbose trajectories to compact operational assets. Verified experience is progressively transformed into SOPs, code, and reusable skills, so improvement appears not only as better policy guidance but also as lower inference-time cost. This is why our evaluation emphasizes efficiency convergence and token reduction under repeated execution, rather than only one-shot task success.

